Multi-wavelength Radio Continuum Emission Studies of Dust-free Red Giants

### 2013-05-06 draft_07/draft.tex
6th May: Edits from Rathmines

\begin{deluxetable}{lcc}
\tabletypesize{\scriptsize}
\tablecaption{Properties of red giant sample.}
\tablehead{	\colhead{}		       				& 
			\colhead{$\alpha$ Boo}				&
			\colhead{$\alpha$ Tau}				}
\startdata
Spectral Type$\dotfill$	& K2 III  & K5 III  \\
HD Number$\dotfill$				& 124897  & 29139  \\
Mass ($M_{\odot}$)$\dotfill$	& $0.8 \pm 0.2$  & $1.3 \pm 0.3$ \\
Effective Temperature (K)$\dotfill$	& $4294 \pm 30$  & $3970 \pm 49$ \\
Angular Diameter (mas)$\dotfill$		& $21.0 \pm 0.2$ & $20.2 \pm 0.3$ \\
Distance (pc)$\dotfill$	& $11.3 \pm 0.1$ & $20.4 \pm 0.3$\\
Radius ($R_{\odot}$)$\dotfill$	& $25.4 \pm 0.3$  & $44.4 \pm 1.0$ \\
Photospheric Escape Velocity$\dotfill$ & 110 km s$^{-1}$ & 106 km s$^{-1}$ \\
%$v \ \times$ sin\textit{i} (km s$^{-1}$)$\dotfill$ & $1.5 \pm 0.3$  & x \\
%$\textit{i}$ (degrees) $\dotfill$ & $58 \pm 25$  & x \\
Rotation Period (yr)$\dotfill$ & $2.0 \pm 0.2$ & 1.8 \\
Wind Terminal Velocity$\dotfill$ & $\sim$40 km s$^{-1}$ & $\sim$30 km s$^{-1}$ \\
Mass Loss Rate ($M_{\odot}$ yr$^{-1}$)$\dotfill$	& 2 $\times$ 10$^{-10}$ & 1.6 $\times$ 10$^{-11}$ \\
Wind Temperature (K)$\dotfill$		& $\sim$10,000  & $<10,000$  \\
Semi-empirical Model$\dotfill$	& \cite{1985pssl.proc..351D} & \cite{1999MNRAS.302...37M}
\enddata
\tablecomments{Masses are from \cite{2010A&A...509A..77K} and \cite{2012A&A...547A.108L}. Effective temperatures and photospheric angular diameters are from \cite{1993AA...270..315D}. Distances are from \cite{2007A&A...474..653V}. Rotaion periods are from \cite{2006PASP..118.1112G} and \cite{1993ApJ...413..339H}. Mass loss rates are from \cite{1985pssl.proc..351D} and \cite{1998ApJ...503..396R}.}

@@

In order to avoid the assumed additional complexities of a companion, we have selected two single luminosity class III red giants: Arcturus ($\alpha$ Boo: K2 III) and Aldebaren ($\alpha$ Tau: K5 III). These nearby red giants have been extensively studied at other wavelengths and their stellar parameters, which are briefly summarized in Table 1, are accurately known. Both of these late-type giants have `hybrid atmospheres' as they show evidence for both coronal/transition region activity and strong winds. Even though they are slow rotators, a magnetic field (albeit weak) has been detected on $\alpha$ Boo \citep{2011A&A...529A.100S} along with a magnetic cycle with a period of $\geq 14$ yr \citep{2008ApJ...679.1531B}, and the detection of O $\textsc{vi}$ in $\alpha$ Tau \citep{2005ApJ...622..629D} suggests magnetic activity in its atmosphere. These stars are predicted to be point sources at all frequencies between 1 and 50 GHz in all VLA configurations so our radio observations measure their total flux density, $F_{\nu}$. Moreover, both stars have existing semi-empirical 1-D chromospheric and wind models which we directly compare to our data in this paper.

@@

\subsection{$\alpha$ Boo Radio Maps} \label{results1} 
High S/N detections ($>19\sigma$) of $\alpha$ Boo were made at 22.5, 33.6, and 43.3 GHz. Some residuals of the dirty beam remained in the CLEANed maps due to the paucity of uv-coverage in these short high frequency observations. At the lower frequencies, it was necessary to image confusing sources, notably a strong radio source located $186\arcsec$ north-west of $\alpha$ Boo. This source was reported by \cite{1986AJ.....91..602D} and their flux density of 25 mJy at 4.9 GHz is in close agreement with our measurement of 23.2 mJy at the same frequency. We find the source to have a spectral index $\alpha$ ($F_{\nu} \propto \nu ^{\alpha}$), equal to -1.4; it reaches 80.3 mJy at 1.6 GHz.

@@

@@

\subsection{Existing Atmospheric Models} \label{disc2}
One of the most important diagnostic features indicating mass outflows in late-type stars are the blue shifted absorption components present in the Mg {\textsc{ii}} h and k resonance lines. Figure \ref{fig:fig0} shows one of the two chromosphere and wind models of $\alpha$ Boo \citep{1985pssl.proc..351D} which is based on the Mg {\textsc{ii}} k 2796 $\rm{\AA}$ emission line taken with the International Ultraviolet Explorer. Both of Drake's atmospheric models contain the photospheric model of \cite{1975ApJ...200..660A} and predict the wind to reach a terminal velocity, $v_{\infty}$, of 35 - 40 km s${}^{-1}$ by 2 $R _{\star}$. They contain a broad temperature plateau with T $\approx$ 8,000 K between 1.2 and $\sim$20 $R _{\star}$ with a cooler region further out, and are $\sim$50\% ionized. We compute the radio spectrum from these models, assuming spherical 1-D geometry and the Gaunt factors from \cite{1988ApJ...327..477H} with free-free and H- free-free opacities are included. The radiative transfer equation is solved using the Feautrier technique \cite[see, e.g.,][]{1994MNRAS.268..894H} and the boundary condition is determined by ensuring the atmosphere is optically thick at the deepest layers. Our computed radio spectrum reproduces Drake's (1985) predicted flux density value of $\sim$0.4 mJy at 6 cm and this is a good check on the robustness of our method of producing radio spectra from these model atmospheres. In reality, substantial departures from spherical symmetry are to be expected in most stellar atmospheres. For example, a global magnetic dipole would cause density variations between the equator and the polar regions. Despite this fact, the study of a  spherically symmetric atmosphere forms the basis of understanding the more complex environments in real stellar atmospheres.

\begin{figure}
\includegraphics[trim = 0mm 0mm 0mm 0mm, clip,scale=0.36,angle=90]{fig0.ps}
\caption{Existing atmospheric model for $\alpha$ Boo \cite[`model A']{1985pssl.proc..351D} along with the same model which undergoes rapid wind cooling beyond $\sim$2.3 $R_{\star}$ (see Section \ref{disc:disc4}). }
\label{fig:fig0}
\end{figure}

\begin{figure*}
\centering
\includegraphics[trim = 0mm 0mm 0mm 20mm, clip,scale=0.65, angle=90]{fig1.ps}
\\
\caption{Spectral energy distribution of $\alpha$ Boo for 1 GHz $\leq \nu \leq$ 1 THz. Our new multi-frequency VLA observations which were mainly acquired over a few days in February 2011 are the blue circles and disagree with the existing chromospheric and wind models of \cite{1985pssl.proc..351D}. The overlap between the two models is represented by the green shaded area. The red diamonds are previous observations which were acquired sporadically over the last three decades with the `old' VLA, IRAM and BIMA. The black dashed line is the expected radio emission from the Drake model which undergoes rapid wind cooling beyond $\sim$2.3 $R_{\star}$ (see Section \ref{disc:disc3} and \ref{disc:disc4}).}
\label{fig:fig1}
\centering
\includegraphics[trim = 0mm 0mm 0mm 20mm, clip,scale=0.65, angle=90]{fig2.ps}
\\
\caption{Spectral energy distribution of $\alpha$ Tau for 1 GHz $\leq \nu \leq$ 1 THz. Our new multi-frequency VLA observations of $\alpha$ Tau (blue circles) were acquired in just two days in February 2011. The red diamonds are the previous radio observations of the star which were acquired over many years. The green line is the expected radio emission from the existing hybrid chromosphere and wind model, while the dashed  green line is the expected radio emission from a theoretical Alfv\'en wave driven model atmosphere.}
\label{fig:fig2}
\end{figure*}

@@

Recently, \cite{2013A&A...553A...3O} has suggested that a layer of CO exists in the outer atmosphere of $\alpha$ Tau (i.e. a so-called MOLsphere) which extends out to $2.5  \ \pm \ 0.3 \ R_{\star}$, has a temperature of $1500 \ \pm 200$ K, a CO column density of $\sim$1$\times 10^{20}$ cm$^{-2}$ and a geometrical extent of 0.1 $R_{\star}$. It can be shown that a MOLsphere with these properties would be optically thick between 3 and 10 cm (i.e. X, C and S-band) if we assume that the electrons in this region of the atmosphere come from singly ionized metals and have an abundance of $\sim 1 \times 10^{-5}\ n_{\rm{H}}$, where $n_{\rm{H}}$ is the total hydrogen number density. Using the assumption then of an optically thick disk with a  spatial extent of 2.5 $R_{\star}$, the expected radio emission at these wavelengths is found to be ~50\% lower than what we actually observe. In the next section we argue that the radio emission from $\alpha$ Tau at these long VLA wavelengths comes from a region much closer in to the star suggesting that the MOLsphere has either a lower column depth or has a much larger geometrical width in order to make it optically thin at these wavelengths.

\subsection{Radio Spectral Indices} \label{disc:disc3}
Long wavelength radio emission from non-dusty K spectral-type red giants is due to thermal free-free emission in their partially ionized outflows while shorter wavelength radio emission may emanate from nearly static lower atmospheric layers. The radio flux density-frequency relationship for this type of stars is always found to be intermediate between that expected from the isothermal stellar disk emission, where $\alpha$ follows the Rayleigh-Jeans tail of the Planck function (i.e., $\alpha = +2$), and that from an optically thin plasma ($\alpha = -0.1$). It can be shown that the expected radio spectrum from a spherically symmetric isothermal outflow with a constant velocity and ionization fraction varies as $\nu ^{0.6}$ \citep{1975MNRAS.170...41W,1975AA....39..217O,1975AA....39....1P}. If we relax some of the assumptions about the outflow in this constant property wind model and instead assume that the electron density and temperature vary as a function of distance from the star $r$, and have the power-law form $n_{e} \propto r^{-p}$ and $T_{e} \propto r^{-n}$ respectively, then

\begin{figure}
\includegraphics[trim = 0mm 0mm 0mm 10mm, clip,scale=0.385,angle=90]{fig3.ps}
\caption{Radio spectra for $\alpha$ Boo and $\alpha$ Tau, together with the best fit power law to their long wavelength flux densities and the resulting spectral indices.}
\label{fig:fig3}
\end{figure}

@@

The higher degree of ionization in the mass outflow of $\alpha$ Boo in comparison to $\alpha$ Tau means that the latter has a substantially smaller effective radius at longer wavelengths, as seen in Figure \ref{fig:fig5}. At 6, 13, and 20 cm the effective radius of $\alpha$ Boo at $\tau _{\rm{rad}}$=1/3 is predicted to be 1.6, 2.8, and 3.7 $R_{\star}$ but is only $\sim$1.2 $R_{\star}$ at 6 and 13 cm for $\alpha$ Tau. \cite{1998ApJ...503..396R} predict that $\alpha$ Tau's wind reaches $\sim$80\% of its terminal velocity by 3 $R_{\star}$, but even our longest-wavelength observations are highly unlikely to sample the wind outside the lower velocity layers closer to the star. For $\alpha$ Boo however, \cite{1985pssl.proc..351D} predicts that the wind has reached its terminal velocity by $\sim$2 $R_{\star}$ so based on this model our longest-wavelength measurements are of the region where the wind has reached a steady terminal velocity. From Figure \ref{fig:fig4}, this implies that the $n_{\rm{e}}$ coefficient $p=2$ and thus the $T_{\rm{e}}$ coefficient $n=1.65$. Pure adiabatic cooling with no heat source has $n=1.33$ so additional cooling operations must be operating, possibly due to recombination of H$^{+}$ and/or line cooling. Finally, if the wind ionization balance has not yet become \textit{frozen-in} in the region of $\alpha$ Boo's wind where the radio emission emanates from then the excess slope of the spectral index could be due to a combination of both cooling and changing ionization fraction. In this scenario the temperature coefficient may be smaller than our derived value because Equation \ref{eq:eq1} assumes a constant ionization fraction.

@@

We adjusted the value of $r_{1}$ to obtain the best fit to our long wavelength observations and found this happened when $r_{1}$ = 2.3 $R_{\star}$. To get this best fit, the existing atmospheric model (i.e. the Drake Model) needed to be adjusted so that it now has a narrower temperature plateau of $T_e = 10,000$ K between 1.2 and 2.3 $R_{\star}$, and a temperature profile and a density profile governed by Equation \ref{eq:eq2} and Equation \ref{eq:eq4} beyond $r_{1}$ = 2.3 $R_{\star}$, respectively. This gives good agreement with our new long wavelength VLA data as shown in Figure \ref{fig:fig1}. This new \textit{hybrid} model which is plotted along with the original Drake model in Figure \ref{fig:fig0}, still has the original ionization fraction of $x_{\rm{HII}} \approx 0.5$ inside 2.3 $R_{\star}$ but now contains an initial rapid decrease in $x_{\rm{HII}}$ post 2.3 $R_{\star}$ which then \textit{freezes-in} to a constant value of $\sim$0.04 beyond $\sim$10 $R_{\star}$.

>>>>

\begin{deluxetable}{lcc}
\tabletypesize{\scriptsize}
\tablecaption{Properties of red giant sample.}
\tablehead{	\colhead{}		       				& 
			\colhead{$\alpha$ Boo}				&
			\colhead{$\alpha$ Tau}				}
\startdata
Spectral Type$\dotfill$	& K2 III  & K5 III  \\
HD Number$\dotfill$				& 124897  & 29139  \\
Mass ($M_{\odot}$)$\dotfill$	& $0.8 \pm 0.2$  & $1.3 \pm 0.3$ \\
Effective Temperature (K)$\dotfill$	& $4294 \pm 30$  & $3970 \pm 49$ \\
Angular Diameter (mas)$\dotfill$		& $21.0 \pm 0.2$ & $20.2 \pm 0.3$ \\
Distance (pc)$\dotfill$	& $11.3 \pm 0.1$ & $20.4 \pm 0.3$\\
Radius ($R_{\odot}$)$\dotfill$	& $25.4 \pm 0.3$  & $44.4 \pm 1.0$ \\
Photospheric Escape Velocity$\dotfill$ & 110 km s$^{-1}$ & 106 km s$^{-1}$ \\
%$v \ \times$ sin\textit{i} (km s$^{-1}$)$\dotfill$ & $1.5 \pm 0.3$  & x \\
%$\textit{i}$ (degrees) $\dotfill$ & $58 \pm 25$  & x \\
Rotation Period (yr)$\dotfill$ & $2.0 \pm 0.2$ & 1.8 \\
Wind Terminal Velocity$\dotfill$ & $\sim$40 km s$^{-1}$ & $\sim$30 km s$^{-1}$ \\
Mass Loss Rate ($M_{\odot}$ yr$^{-1}$)$\dotfill$	& 2 $\times$ 10$^{-10}$ & 1.6 $\times$ 10$^{-11}$ \\
Wind Temperature (K)$\dotfill$		& $\sim$10,000  & $<$10,000  \\
Semi-empirical Model$\dotfill$	& \cite{1985pssl.proc..351D} & \cite{1999MNRAS.302...37M}
\enddata
\tablecomments{Masses are from \cite{2010A&A...509A..77K} and \cite{2012A&A...547A.108L}. Effective temperatures and photospheric angular diameters are from \cite{1993AA...270..315D}. Distances are from \cite{2007A&A...474..653V}. Rotaion periods are from \cite{2006PASP..118.1112G} and \cite{1993ApJ...413..339H}. Mass loss rates are from \cite{1985pssl.proc..351D} and \cite{1998ApJ...503..396R}.}

@@

In order to avoid the assumed additional complexities of a companion, we have selected two single luminosity class III red giants: Arcturus ($\alpha$ Boo: K2 III) and Aldebaren ($\alpha$ Tau: K5 III). These nearby red giants have been extensively studied at other wavelengths and their stellar parameters, which are briefly summarized in Table 1, are accurately known. Both of these late-type giants have `hybrid atmospheres' as they show evidence for both coronal/transition region activity and strong winds. Even though they are slow rotators, a magnetic field (albeit weak) has been detected on $\alpha$ Boo \citep{2011A&A...529A.100S} along with a magnetic cycle with a period of $\geq$14 yr \citep{2008ApJ...679.1531B}. Also, the detection of O $\textsc{vi}$ in $\alpha$ Tau \citep{2005ApJ...622..629D} suggests magnetic activity in its atmosphere. These stars are predicted to be point sources at all frequencies between 1 and 50 GHz in all VLA configurations so our radio observations measure their total flux density, $F_{\nu}$. Moreover, both stars have existing semi-empirical 1-D chromospheric and wind models which we directly compare to our data in this paper.

@@

\subsection{$\alpha$ Boo Radio Maps} \label{results1} 
High S/N detections ($>19\sigma$) of $\alpha$ Boo were made at 22.5, 33.6, and 43.3 GHz. Some residuals of the dirty beam remained in the CLEANed maps due to the paucity of uv-coverage in these short high frequency observations. At the lower frequencies, it was necessary to image confusing sources, notably a strong radio source located $186\arcsec$ north-west of $\alpha$ Boo. This source was reported by \cite{1986AJ.....91..602D} and their flux density of 25 mJy at 4.9 GHz is in close agreement with our measurement of 23.2 mJy at the same frequency. We find the source to have a spectral index $\alpha$ ($F_{\nu} \propto \nu ^{\alpha}$), equal to -1.4 and reaches 80.3 mJy at 1.6 GHz.

@@

\begin{figure*}
\centering
\includegraphics[trim = 0mm 0mm 0mm 20mm, clip,scale=0.65, angle=90]{fig0.ps}
\\
\caption{Spectral energy distribution of $\alpha$ Boo for 1 GHz $\leq \nu \leq$ 1 THz. Our new multi-frequency VLA observations which were mainly acquired over a few days in February 2011 are the blue circles and disagree with the existing chromospheric and wind models of \cite{1985pssl.proc..351D}. The overlap between the two models is represented by the green shaded area. The red diamonds are previous observations which were acquired sporadically over the last three decades with the `old' VLA, IRAM and BIMA. The black dashed line is the expected radio emission from the Drake model which undergoes rapid wind cooling beyond $\sim$2.3 $R_{\star}$ (see Section \ref{disc:disc3} and \ref{disc:disc4}).}
\label{fig:fig1}
\centering
\includegraphics[trim = 0mm 0mm 0mm 20mm, clip,scale=0.65, angle=90]{fig1.ps}
\\
\caption{Spectral energy distribution of $\alpha$ Tau for 1 GHz $\leq \nu \leq$ 1 THz. Our new multi-frequency VLA observations of $\alpha$ Tau (blue circles) were acquired in just two days in February 2011. The red diamonds are the previous radio observations of the star which were acquired over many years. The green line is the expected radio emission from the existing hybrid chromosphere and wind model, while the dashed  green line is the expected radio emission from a theoretical Alfv\'en wave driven model atmosphere.}
\label{fig:fig2}
\end{figure*}

@@

\subsection{Existing Atmospheric Models} \label{disc2}
One of the most important diagnostic features indicating mass outflows in late-type evolved stars are the blue shifted absorption components present in the Mg {\textsc{ii}} h and k resonance lines. Figure \ref{fig:fig0} shows one of the two chromosphere and wind models of $\alpha$ Boo \citep{1985pssl.proc..351D} which is based on the Mg {\textsc{ii}} k 2796 $\rm{\AA}$ emission line taken with the International Ultraviolet Explorer. Both of Drake's atmospheric models contain the photospheric model of \cite{1975ApJ...200..660A} and predict the wind to reach a terminal velocity of 35 - 40 km s${}^{-1}$ by 2 $R _{\star}$. They contain a broad temperature plateau with T $\approx$ 8,000 K between 1.2 and $\sim$20 $R _{\star}$ with a cooler region further out, and are 50\% ionized. We compute the expected radio spectrum from these models, assuming spherical 1-D geometry and the Gaunt factors from \cite{1988ApJ...327..477H} with free-free and H- free-free opacities are included. The radiative transfer equation is solved using the Feautrier technique \cite[see, e.g.,][]{1994MNRAS.268..894H} and the boundary condition is determined by ensuring the atmosphere is optically thick at the deepest layers. Our computed radio spectrum reproduces Drake's (1985) predicted flux density value of $\sim$0.4 mJy at 6 cm and this is a good check on the robustness of our method of producing radio spectra from these model atmospheres. In reality, substantial departures from spherical symmetry are to be expected in most stellar atmospheres. For example, a global magnetic dipole would cause density variations between the equator and the polar regions. Despite this fact, the study of a  spherically symmetric atmosphere forms the basis of understanding the more complex environments in real stellar atmospheres.

\begin{figure}
\includegraphics[trim = 0mm 0mm 0mm 0mm, clip,scale=0.36,angle=90]{fig2.ps}
\caption{Existing atmospheric model for $\alpha$ Boo \cite[`model A']{1985pssl.proc..351D} along with the same model which undergoes rapid wind cooling beyond $\sim$2.3 $R_{\star}$ (see Section \ref{disc:disc4}). The original Drake Model has a temperature plateau of $\sim$8,000 K between 1.2 and $\sim$ 20 $R_{\star}$ (solid black line), reaches a terminal velocity of 35-40 km s$^{-1}$ within 2 $R_{\star}$ (solid green line), and has a wind which is 50\% ionized (dashed and dotted black lines).}
\label{fig:fig0}
\end{figure}

@@

Recently, \cite{2013A&A...553A...3O} has found that a layer of CO exists in the outer atmosphere of $\alpha$ Tau (i.e. a so-called MOLsphere) which extends out to $2.5  \ \pm \ 0.3 \ R_{\star}$, has a temperature of $1500 \ \pm 200$ K, a CO column density of $\sim$1$\times 10^{20}$ cm$^{-2}$ and a geometrical extent of 0.1 $R_{\star}$. It can be shown that a MOLsphere with these properties would be optically thick between 3 and 10 cm (i.e. X, C and S-band) if we conservatively assume that the electrons in this region of the atmosphere come from singly ionized metals and have an abundance of $\sim$1$\times 10^{-5} n_{\rm{H}}$, where $n_{\rm{H}}$ is the total hydrogen number density. Using the assumption then of an optically thick disk with a  spatial extent of 2.5 $R_{\star}$, the expected radio emission at these wavelengths is found to be ~50\% lower than what we actually observe. In the next section we argue that the radio emission from $\alpha$ Tau at these long VLA wavelengths comes from a region much closer in to the star suggesting that the MOLsphere has either a lower column depth or has a much larger geometrical width in order to make it optically thin at these wavelengths.

\subsection{Radio Spectral Indices} \label{disc:disc3}
Long wavelength radio emission from non-dusty K spectral-type red giants is due to thermal free-free emission in their partially ionized outflows while shorter wavelength radio emission may emanate from nearly static lower atmospheric layers. The radio flux density-frequency relationship for these stars is usually found to be intermediate between that expected from the isothermal stellar disk emission, where $\alpha$ follows the Rayleigh-Jeans tail of the Planck function (i.e., $\alpha = +2$), and that from an optically thin plasma ($\alpha = -0.1$). It can be shown that the expected radio spectrum from a spherically symmetric isothermal outflow with a constant velocity and ionization fraction varies as $\nu ^{0.6}$ \citep{1975MNRAS.170...41W,1975AA....39..217O,1975AA....39....1P}. If we relax some of the assumptions about the outflow in this constant property wind model and instead assume that the electron density and temperature vary as a function of distance from the star $r$, and have the power-law form $n_{e} \propto r^{-p}$ and $T_{e} \propto r^{-n}$ respectively, then

\begin{figure}
\includegraphics[trim = 0mm 0mm 0mm 10mm, clip,scale=0.385,angle=90]{fig3.ps}
\caption{Radio spectra for $\alpha$ Boo and $\alpha$ Tau, together with the best fit power law to their long wavelength flux densities and the resulting spectral indices. The spectral index for $\alpha$ Boo and $\alpha$ Tau are found to be 1.05 and 1.58, respectively, which are both larger than the 0.6 value expected for a constant property wind model.}
\label{fig:fig3}
\end{figure}

@@

The higher degree of ionization in the mass outflow of $\alpha$ Boo in comparison to $\alpha$ Tau means that the latter has a substantially smaller effective radius at longer wavelengths, as seen in Figure \ref{fig:fig5}. At 6, 13, and 20 cm the effective radius of $\alpha$ Boo at $\tau _{\rm{rad}}$=1/3 is predicted to be 1.6, 2.8, and 3.7 $R_{\star}$ but is only $\sim$1.2 $R_{\star}$ at 6 and 13 cm for $\alpha$ Tau. \cite{1998ApJ...503..396R} predict that $\alpha$ Tau's wind reaches $\sim$80\% of its terminal velocity by 3 $R_{\star}$, but even our longest-wavelength observations are highly unlikely to sample the wind outside the lower velocity layers closer to the star. For $\alpha$ Boo however, \cite{1985pssl.proc..351D} predicts that the wind has reached its terminal velocity by $\sim$2 $R_{\star}$ so based on this model our longest-wavelength measurements are of the region where the wind has reached a steady terminal velocity. From Figure \ref{fig:fig4}, this implies that the $n_{\rm{e}}$ coefficient $p=2$ and thus the $T_{\rm{e}}$ coefficient $n=1.65$. Pure adiabatic cooling with no heat source has $n=1.33$ so additional cooling operations must be operating, possibly due to recombination of H$^{+}$ and/or line cooling. Finally, if the wind ionization balance has not yet become \textit{frozen-in} in the region of $\alpha$ Boo's wind where the radio emission emanates from then the excess slope of the spectral index could be due to a combination of both cooling and changing ionization fraction. In this scenario the temperature coefficient $n$, may be smaller than our derived value because Equation \ref{eq:eq1} assumes a constant ionization fraction.

@@

We adjusted the value of $r_{1}$ to obtain the best fit to our long wavelength observations and found this happened when $r_{1}$ = 2.3 $R_{\star}$. To get this best fit, the existing atmospheric model (plotted in Figure \ref{fig:fig0}) needed to be adjusted so that it now has a narrower and slightly larger temperature plateau of $T_e = 10,000$ K between 1.2 and 2.3 $R_{\star}$, and a temperature profile and a density profile governed by Equation \ref{eq:eq2} and Equation \ref{eq:eq4} beyond $r_{1}$ = 2.3 $R_{\star}$, respectively. This gives good agreement with our new long wavelength VLA data as shown in Figure \ref{fig:fig1}. This new \textit{hybrid} model which is plotted along with the original Drake model in Figure \ref{fig:fig0}, still has the original ionization fraction of $x_{\rm{HII}} \approx 0.5$ inside 2.3 $R_{\star}$ but now contains an initial rapid decrease in $x_{\rm{HII}}$ post 2.3 $R_{\star}$ which then \textit{freezes-in} to a constant value of $\sim$0.04 beyond $\sim$10 $R_{\star}$.
